---
title: "Simple document"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
---

```{r}
library(tidyverse)
```


I'm an R Markdown document! 

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r round(mean(samp), 3)`.

# Section 3

## Plot from last time

This is going to make a plot! First generate a dataframe, then use `ggplot` to make a scatterplot.

```{r chunk_scatterplot, echo = FALSE}
plot_df =
  tibble(
    x = rnorm(n = 1000),
    y = 1 + 2 * x + rnorm(n=1000)
  )
```

```{r chuntk_histogram}
ggplot(plot_df, aes(x = x, y = y)) + geom_point()
```

## Plot from LA

This is a quick kind of solution to the LA: Write a named code chunk that creates a dataframe comprised of: a numeric variable containing a random sample of size 500 from a normal variable with mean 1; a logical vector indicating whether each sampled value is greater than zero; and a numeric vector containing the absolute value of each element. Then, produce a histogram of the absolute value variable just created. Add an inline summary giving the median value rounded to two decimal places.

```{r learning_assessment}
la_df =
  tibble(
    norm = rnorm(n = 500, mean = 1),
    logical = norm > 0,
    abs_norm = abs(norm)
  )

ggplot(la_df, aes(x = abs_norm)) + geom_histogram()
```
